Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Add small precision about valid entries in XP2
Updates from Overleaf

We leverage the labeled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Kraken is left aside as it produces poor results that would require removing 500 entries from all datasets to keep the same set of valid entries.

Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain 8341 entries, the produced train sets (resp. development and test) contain 6004 entries - 72\% of the total (resp. 668 - 8\% and 1669 - 20\%).

>>>>

We leverage the labeled sets of entries NER-\emph{reference}, NER-\emph{pero} and NER-\emph{tesseract} created as explained in \cref{sec:dataset}.
Each dataset is split into training development, and test sets following the same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain 8341 entries (see \cref{sec:dataset-for-eval}), the produced train sets (resp. development and test) contain 6004 entries - 72\% of the total (resp. 668 - 8\% and 1669 - 20\%).
